Universal Understanding of the Dielectric Nature of Two-Dimensional Materials

### 2018-11-15 SI.tex
Add optical bandgap in SI

% Created 2017-10-05 Thu 16:11
% Intended LaTeX compiler: pdflatex
\documentclass[manuscript=suppinfo,email=true,hyperref=true,keywords=false]{achemso}
\usepackage{times}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage[T1]{fontenc}
\usepackage{ltablex}
\usepackage{footnote}
\usepackage[colorinlistoftodos,prependcaption,textsize=small]{todonotes}

\usepackage{float}

@@

\author{Tian Tian}
\affiliation{Institute for Chemical and Bioengineering, ETH Z{\"{u}}rich,  Vladimir Prelog Weg 1, CH-8093 Z{\"{u}}rich, Switzerland}
\altaffiliation{T. T. and D. S. contributed equally to this work}
\author{Declan Scullion}
\affiliation{School of Mathematics and Physics, Queen's University Belfast, BT7 1NN, United Kingdom}
\altaffiliation{T. T. and D. S. contributed equally to this work}
\author{Dale Hughes}
\affiliation{School of Mathematics and Physics, Queen's University Belfast, BT7 1NN, United Kingdom}
\author{Lu Hua Li}
\affiliation{Institute for Frontier Materials, Deakin University, Waurn Ponds, Victoria, Australia}
\author{Chih-Jen Shih}
\affiliation{Institute for Chemical and Bioengineering, ETH Z{\"{u}}rich,  Vladimir Prelog Weg 1, CH-8093 Z{\"{u}}rich, Switzerland}
\author{Jonathan Coleman}
\affiliation{School of Physics, Centre for Research on Adaptive Nanostructures and Nanodevices (CRANN) and Advanced Materials and BioEngineering Research (AMBER), Trinity College Dublin, Dublin 2, Ireland.}
\author{Manish Chhowalla}
\affiliation{Materials Science and Engineering, Rutgers University, 607 Taylor Road, Piscataway, New Jersey 08854, USA.}
\author{Elton J. G. Santos}
\email{e.santos@qub.ac.uk}
\affiliation{School of Mathematics and Physics, Queen's University Belfast, BT7 1NN, United Kingdom}

@@

\section{Hypothetical 2D dielectric constant rescaled from 3D dielectric constant}
\label{sec:2D-3D-rescale}

From literatures, it is often desired to extract the ``dielectric
constant'' of a 2D material from the 3D macroscopic dielectric
constant of the superlattice, where the layers are periodic along of
x,y directions but separated by a vacuum layer between its images
\cite{Matthes_2016,Laturia_2018}. As discussed in the main text, the
definition of the 2D ``dielectric constant'' (in particular, its
in-plane components) is questionable, due to the locality of
electrostatic screening of the 2D materials
\cite{Cudazzo_2010_screen2D,Cudazzo_2011_screening_2D}. Here we show
that, in addition to the ambiguous definition of the 2D dielectric
constant, such approach requires the precise determination of the 2D
layer thickness $\delta_{\mathrm{2D}}$, which makes it impractical.

@@

\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.95\linewidth]{img/SI-rescale-PRB.pdf}
  \caption{ Calculated (blue dots) and fitted
    (orange broken lines) $\varepsilon_{\mathrm{SL}}$ as function of
    $L$ for the group 6 TMDCs:
    \textbf{a}. MoS$_{2}$. \textbf{b}. MoSe$_{2}$. \textbf{c}.
    MoTe$_{2}$. \textbf{d}. WS$_{2}$. \textbf{e}. WSe$_{2}$. \textbf{f}.
    WTe$_{2}$. The extracted values of $\varepsilon_{\mathrm{2D}}$ and
    $\delta$ are shown in each subfigure.}
  \label{fig:rescale-prb}
\end{figure}

@@

\begin{table}[htbp]
  \centering
  \begin{tabular}[htbp]{lccccc}
  \hline{}
  Material & $\delta_{\mathrm{2D}}$ from $\varepsilon_{\mathrm{SL}}^{\parallel}$ ({\AA}) & $\delta_{\mathrm{2D}}$ from $\varepsilon_{\mathrm{SL}}^{\perp}$ ({\AA})& $L_{\mathrm{bulk}}$ ({\AA}) & $\delta_{\mathrm{2D}}^{\mathrm{cov}}$ ({\AA}) & $\alpha^{\perp}/\varepsilon_{0}$ ({\AA})\\
  \hline{}
  2H-MoS$_{2}$ & 5.76 & 5.49 & 6.15 & 5.22 & 4.98\\
  2H-MoSe$_{2}$ & 5.98 & 5.92 & 6.46 &  5.73 & 5.60\\
  2H-MoTe$_{2}$ & 6.43 & 6.85 & 6.98 & 6.37 & 6.12\\
  2H-WS$_{2}$ & 5.63 & 5.49 & 6.15 & 5.20 & 5.00\\
  2H-WSe$_{2}$ & 5.84 & 5.92 & 6.49 & 5.75 & 5.42\\
  2H-WTe$_{2}$ & 6.32 & 6.58 & 7.06 & 6.38 & 6.33\\
  \hline{}
\end{tabular}

\caption{Calculated $\delta_{\mathrm{2D}}$ from
  $\varepsilon_{\mathrm{SL}}^{\parallel}$ and
  $\varepsilon_{\mathrm{SL}}^{\perp}$, compared with the interlayer
  distance of corresponding bulk material $L_{\mathrm{SL}}$, the
  covalent thickness $\delta_{\mathrm{2D}}^{\mathrm{cov}}$, and
  $\alpha^{\perp}/\varepsilon_{0}$ for 2H TMDC materials.}
\label{tab:delta-L-DFt}
\end{table}

Another drawback of the 2D dielectric constant approach is the
overestimation of the out-of-plane dielectric response. As can be seen
in Figure \ref{fig:rescale-prb}, the extracted
$\varepsilon_{\mathrm{2D}}^{\perp}$ values for the TMDCs studied
are comparable or even larger than
$\varepsilon_{\mathrm{2D}}^{\parallel}$, which does not agree with the
physical picture that electrostatic screening of 2D materials are much
smaller perpendicular to the 2D plane. In fact, combining
Eq. \ref{eq:MG-effect-1} and the definition of $\alpha^{\perp}$, we
have:
\begin{equation}
  \label{eq:eps-alpha-perp}
  \frac{\alpha^{\perp}}{\varepsilon_{0}} = \delta_{\mathrm{2D}}(1 - (\varepsilon_{\mathrm{2D}}^{\perp})^{-1})
\end{equation}

\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.7\linewidth]{img/SI-eps-alpha-error.pdf}
  \caption{Calculated $\varepsilon_{\mathrm{2D}}^{\perp}$ value as a
    function of the difference between $\delta_{\mathrm{2D}}$ and
    $\alpha^{\perp}/\varepsilon_{0}$. A small change of
    $\alpha^{\perp}/\varepsilon_{0}$ chosen may lead to divergence of
    the $\varepsilon_{\mathrm{2D}}^{\perp}$ or even negative values,
    which is apparently unphysical}
  \label{fig:eps-alpha-error}
\end{figure}

which indicate that the characteristic length
$\alpha^{\perp}/\varepsilon_{0}$, is very close but slightly smaller
than $\delta_{\mathrm{2D}}$ estimated by the effective medium theory,
if $\varepsilon^{\perp}_{\mathrm{2D}} \gg 1$. Moreover, from
Eq. \ref{eq:eps-alpha-perp}, when $\delta_{\mathrm{2D}}$ and
$\alpha^{\perp}/\varepsilon_{0}$ are close, slight change of the
$\delta_{\mathrm{2D}}$ chosen may lead to divergence of
$\varepsilon_{\mathrm{2D}}^{\perp}$, as shown in Figure
\ref{fig:eps-alpha-error}. Therefore cautions must to taken when
treating the dielectric response of the 2D material using effective
medium theory. In comparison, the 2D polarizability does not require
the guess of the thickness, and therefore is the true descriptor of
the 2D dielectric nature.

To conclude, based on theoretical and technical considerations, there are several
advantages of using the polarizability $\alpha$ for describing the dielectric
nature of 2D materials, including
\begin{enumerate}
\item $\alpha$ can be used to describe both the local and macroscopic dielectric properties, while $\epsilon_{\mathrm{2D}}$ can't.
\item Calculating $\alpha$ only requires to calculate the dielectric response at single superlattice length, while $\epsilon_{\mathrm{2D}}$ requires calculation with varied superlattice length.
\item $\alpha$ correctly respresents the screening length of 2D material, while $\epsilon_{\mathrm{2D}}$ does not.
\item $\alpha$ correctly represents the different degree of screening in/out-of-plane, while $\epsilon_{\mathrm{2D}}$ does not.

\item The value of $\epsilon_{\mathrm{2D}}$ hugely depends on the
  choice of the thickness of 2D material, while such information is
  intrinsically embedded in $\alpha$.
\end{enumerate}

\section{Further analysis of the 2D polarizability}
\label{sec:pol-2D}

In this section we will provide more analysis on the 2D polarizability
in addition to the main text.

\subsection{Dependence of superlattice size}
\label{sec:pol-2D-1}

We study the polarizabilties of group 6 TMDCs to demonstrate the
dependency between the 2D polarizability $\alpha$ and the superlattice
length $L$, which is shown in Figure \ref{fig:eps-L-all}.  In all cases, we observe that the calculated
polarizability converges when $L>$15 \AA{}, in good agreement with our
conclusion in main text. The lower bound of $L_{\mathrm{min}}$ for the
convergence of $\alpha$ can be viewed as the minimal distance that
overlap of induced charge density from image layers is negligible. In
practice, any superlattice size larger than $L_{\mathrm{min}}$ can be
used for calculating the intrinsic 2D dielectric nature through the
polarizability, however to reduce the computational cost, especially
at the HSE06 level, we typically choose a superlattice size no larger
than 35 \AA{}.

\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.95\linewidth]{img/SI-eps-L-all.pdf} 
  \caption{Calculated value of $\varepsilon_{\mathrm{SL}}^{\parallel}$
    (top left axis), $\varepsilon_{\mathrm{SL}}^{\perp}$ (bottom left
    axis), $\alpha^{\parallel}$ (top right axis) and $\alpha^{\perp}$
    (bottom right axis) of various group 6 TMDCs corresponding to
    Figure 1 in main text. In all cases, the polarizability converges
    when $L>$15 \AA{}}
  \label{fig:eps-L-all}
\end{figure}

\subsection{Dependence of bandgap}
\label{sec:pol-2D-2}

In this section we further look into the bandgap dependency of the 2D
polarizability. Figure \ref{fig:SI-raw-HSE} shows $\alpha^{\parallel}$
and $\alpha^{\perp}$ as functions of $E_{\mathrm{g}}$ of the 2D
materials studied here. We observe that $\alpha^{\parallel}$ can be
approximated by a reciprocal function of $E_{\mathrm{g}}$, that
$\alpha^{\parallel}\sim{} 7.295(E_{\mathrm{g}})^{-1}$. On the other
hand, the plot of $\alpha^{\perp}$ against $E_{\mathrm{g}}$ shows no
apparent correlation.
\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.8\linewidth]{img/SI-alpha_EG_raw_HSE.pdf}
  \caption{$E_{\mathrm{g}}$-dependence of    \textbf{a} $\alpha^{\parallel}$ and
    \textbf{b} $\alpha^{\perp}$ for the 2D materials investigated here.}
  \label{fig:SI-raw-HSE}
\end{figure}

\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.5\linewidth]{img/SI-compare_alpha_Eg.pdf}
  \caption{Relation between $1/\alpha^{\parallel}$ and various choices
    of $E_{\mathrm{g}}$: minimal gap from HSE06 (blue), minimal gap
    from PBE (orange) and direct gap from PBE (green). The linear
    regression results are shown as broken lines.}
  \label{fig:alpha-Eg-diff}
\end{figure}

We also investigate the relation of 2D polarizabilities with
difference choices of \textit{ab initio} bandgaps. It is widely
accepted that the PBE exchange correlation, tends to underestimate the
bangap \cite{Heyd_2005,Kumar_2016_PRB,Kumar_2016_jpcc}.  Indeed,
changing the choice of $E_{\mathrm{g}}$ yields different regression
relation with $1/\alpha^{\parallel}$, as shown in Figure
\ref{fig:alpha-Eg-diff}. We see that due to the underestimation of PBE
bandgap, the slope of linear regression is larger than that from
HSE-bandgap. We also observe that the $1/\alpha-E_{\mathrm{g}}$
relation is better presented by using the minimal HSE bandga than the
minimal PBE bandgap, due to higher regression $R^{2}$ coefficient of
the former. We note that the higher $R^{2}$ coefficient observed using
the direct PBE bandgap than the minimal PBE bandgap may be solely
caused by the fact that the direct bandgap of 2D materials on the PBE
level is closer to the HSE bandgap. From the random phase
approximation theory of dielectric response, the polarizability is
contributed by all possible transition between valence and conduction
bands, with the minimal bandgap as the least possible transition. In
this sense, $\alpha^{\parallel}$ is mostly like to be associated with
the minimal, not direct bandgap, as also observed in the original Moss
relation. We also examine the validity of such statement based on the
analysis of the Computational 2D Materials Database (C2DB)
\cite{Haastrup_2018}, as will be discussed in the following sections.

\section{Validation on the C2DB 2D materials database}
\label{sec:gpaw}
\subsection{Validation of the universal description of 2D polarizabilities}
\label{sec:gpaw-1}

\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.8\linewidth]{img/SI-gpaw-data.pdf}
  \caption{Validation the linear relation between \textbf{a}
    $1/\alpha^{\parallel}-E_{\mathrm{g}}(\mathrm{HSE})$ and \textbf{b}
    $\alpha^{\perp}-\delta_{\mathrm{cov}}$ on the C2DB 2D material
    database, corresponding to Figure 3b and 3c in main text.}
  \label{fig:gpaw-alpha-relation}
\end{figure}

Due to the high computation complexity of dielectric response
calculations on the HSE level, our 2D material database is limited to
about 50 types of materials. It is desirable to validate our proposed
relations on a even larger scale database. We select over 230
semiconducting 2D materials from the C2DB database with a GW bandgap
larger than 0.05 eV and extracted the 2D polarizabilities calculated
on the PBE level. The propsed linear relations between
$1/\alpha^{\parallel}-E_{\mathrm{g}}(\mathrm{HSE})$ and
$\alpha^{\perp}-\delta_{\mathrm{cov}}$ are also valid,
as shown in Figure \ref{fig:gpaw-alpha-relation}. Excellent linear
correlation is observed in both cases, with the $R^{2}$ coefficient
larger than 0.9, indicating the existence of the universal description
of 2D dielectric nature through the proposed relations with the 2D
polarizabilities. We note that the slope of linear regression is
slightly different from the our proposed relation from the dielectric
response on HSE06 level, due to the fact that the macroscopic
dielectric constant $\varepsilon_{\mathrm{SL}}$ calculated on the PBE
level is about slightly difference. Despite the minor deviation of the
slope of linear regression, the analysis on the C2DB database supports
our understanding of the universal dielectric nature of 2D materials.

@@

Next we investigate the influence of choice of $E_{\mathrm{g}}$ on the
regression of $\alpha^{\parallel}-E_{\mathrm{g}}$ relation. Figure
\ref{fig:SI-gpaw-alpha-Eg-all} shows $1/\alpha^{\parallel}$ from the
C2DB database as a function of minimal and direct bandgap calculated
on PBE, HSE06 and GW levels. We observe,
although the regression $R^{2}$ coefficient in all cases are around
0.9, the $\alpha^{\parallel}-E_{\mathrm{g}}$ is better described using
the HSE and GW bandgaps than the PBE bandgaps. On the other hand,
using indirect or minimal bandgaps on the same level gives almost
identical regression slope. The observations are in good agreement
with our calculations on the HSE level discussed in Section
\ref{sec:pol-2D-2}. In combination with the physical contribution of
$E_{\mathrm{g}}$ to the dielectric screening, we conclude that the
minimal bandgap should be used for quantitative prediction of the
in-plane 2D polarizability. The prediction is greatly improved when
more accurate theory level for bandgap is used (for instance, HSE and GW).

\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.95\linewidth]{img/SI-gpaw-alpha_Eg_all.pdf}
  \caption{$\alpha^{\parallel}$ as funtion of minimal and direct
    $E_{\mathrm{g}}$ calculated on different theoretical levels:
    \textbf{a} PBE, \textbf{b} HSE and \textbf{c} GW of the C2DB
    database.}
  \label{fig:SI-gpaw-alpha-Eg-all}
\end{figure}

>>>>

% Created 2017-10-05 Thu 16:11
% Intended LaTeX compiler: pdflatex
\documentclass[manuscript=suppinfo,email=true,hyperref=true,keywords=false]{achemso}
\usepackage{times}
\usepackage{float}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage[T1]{fontenc}
\usepackage{ltablex}
\usepackage{footnote}
\usepackage[colorinlistoftodos,prependcaption,textsize=small]{todonotes}

\usepackage{xr}
\externaldocument[main-]{paper}

@@

\author{Tian Tian}
\affiliation{Institute for Chemical and Bioengineering, ETH Z{\"{u}}rich,  Vladimir Prelog Weg 1, CH-8093 Z{\"{u}}rich, Switzerland}
\altaffiliation{T. T. and D. S. contributed equally to this work}
\author{Declan Scullion}
\affiliation{School of Mathematics and Physics, Queen's University Belfast, BT7 1NN, United Kingdom}
\altaffiliation{T. T. and D. S. contributed equally to this work}
\author{Dale Hughes}
\affiliation{School of Mathematics and Physics, Queen's University Belfast, BT7 1NN, United Kingdom}
\author{Lu Hua Li}
\affiliation{Institute for Frontier Materials, Deakin University, Waurn Ponds, Victoria, Australia}
\author{Chih-Jen Shih}
\affiliation{Institute for Chemical and Bioengineering, ETH Z{\"{u}}rich,  Vladimir Prelog Weg 1, CH-8093 Z{\"{u}}rich, Switzerland}
\author{Jonathan Coleman}
\affiliation{School of Physics, Centre for Research on Adaptive Nanostructures and Nanodevices (CRANN) and Advanced Materials and BioEngineering Research (AMBER), Trinity College Dublin, Dublin 2, Ireland.}
\author{Manish Chhowalla}
% \affiliation{Materials Science and Engineering, Rutgers University, 607 Taylor Road, Piscataway, New Jersey 08854, USA.}
\affiliation{Department of Materials Science \& Metallurgy, University of Cambridge, CB3 0FS, United Kindom}
\author{Elton J. G. Santos}
\email{e.santos@qub.ac.uk}
\affiliation{School of Mathematics and Physics, Queen's University Belfast, BT7 1NN, United Kingdom}

@@

\newpage{}
\section{Further Analysis of the 2D Polarizability Model}
\label{sec:2D-pol}

In this section, we discuss further topics about the 2D polarizability
model proposed in the main text.

\subsection{Profile of induced dipoles of 2D material}
\label{sec:dipole-plot}
Here we show in detail the
$\Delta \rho=\rho(\boldsymbol{E}) - \rho(\boldsymbol{E}=0)$ profile of
the 2H-MoS$_{2}$ slab in main text Figure \ref{main-fig-1}a. The
density $\rho$ is calculated as the average value in the
\textit{xy}-plane, and the value is shown in Figure
\ref{fig:rho-profile}. As can be seen the induced charges on the
MoS$_{2}$ layer only extends to a width of $\sim{}$12 \AA{}. When the
SL size $L \gg$12 \AA{} as in the first principle calculations done in
the main text, the induced dipoles from the periodic images do not
interact, and thus giving converged values of $\alpha_{\mathrm{2D}}$.

\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.95\linewidth]{img/SI-dipole-MoS2.pdf}
  \caption{Induced dipole profile of a 2H-MoS$_{2}$ slab inside the
    superlattice, corresponding to main text Figure
    \ref{main-fig-1}a. \textbf{a}. Scheme of the MoS$_{2}$ layer
    inside the SL separated by vacuum layer. The dielectric constant
    $\varepsilon_{\mathrm{SL}}$ is combined effect of the 2D
    polarizability $\alpha_{\mathrm{2D}}$ and the vacuum
    layer. \textbf{b}. $\Delta \rho$ as a function of $z$ around the
    MoS$_{2}$ layer, green and red parts corresponding to negative and
    positive induced charges. The external electric field
    $E_{\mathrm{ext}}$ is 0.01 eV/\AA{}.}
  \label{fig:rho-profile}
\end{figure}

\subsection{Hypothetical 2D ``dielectric constant'' rescaled from 3D dielectric constant}
\label{sec:2D-3D-rescale}
From literatures, it is often desired to extract the ``dielectric
constant'' of a 2D material from the 3D macroscopic dielectric
constant of the superlattice, where the layers are periodic along of
x,y directions but separated by a vacuum layer between its images
\cite{Matthes_2016,Laturia_2018}. As discussed in the main text, the
definition of the 2D ``dielectric constant'' (in particular, its
in-plane components) is questionable, due to the locality of
electrostatic screening of the 2D materials
\cite{Cudazzo_2010_screen2D,Cudazzo_2011_screening_2D}. Here we show
that, in addition to the ambiguous definition of the 2D dielectric
constant, such approach requires the precise determination of the 2D
layer thickness $\delta_{\mathrm{2D}}$, which makes it impractical.

@@

\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.85\linewidth]{img/SI-rescale-PRB.pdf}
  \caption{ Calculated (blue dots) and fitted
    (orange broken lines) $\varepsilon_{\mathrm{SL}}$ as function of
    $L$ for the group 6 TMDCs:
    \textbf{a}. MoS$_{2}$. \textbf{b}. MoSe$_{2}$. \textbf{c}.
    MoTe$_{2}$. \textbf{d}. WS$_{2}$. \textbf{e}. WSe$_{2}$. \textbf{f}.
    WTe$_{2}$. The extracted values of $\varepsilon_{\mathrm{2D}}$ and
    $\delta$ are shown in each subfigure.}
  \label{fig:rescale-prb}
\end{figure}

@@

\begin{table}[htbp]
  \centering
  \begin{tabular}[htbp]{lccccc}
  \hline{}
  Material & $\delta_{\mathrm{2D}}$ from $\varepsilon_{\mathrm{SL}}^{\parallel}$ ({\AA}) & $\delta_{\mathrm{2D}}$ from $\varepsilon_{\mathrm{SL}}^{\perp}$ ({\AA})& $L_{\mathrm{bulk}}$ ({\AA}) & $\delta_{\mathrm{2D}}^{\mathrm{cov}}$ ({\AA}) & $\alpha_{\mathrm{2D}}^{\perp}/\varepsilon_{0}$ ({\AA})\\
  \hline{}
  2H-MoS$_{2}$ & 5.76 & 5.49 & 6.15 & 5.22 & 4.98\\
  2H-MoSe$_{2}$ & 5.98 & 5.92 & 6.46 &  5.73 & 5.60\\
  2H-MoTe$_{2}$ & 6.43 & 6.85 & 6.98 & 6.37 & 6.12\\
  2H-WS$_{2}$ & 5.63 & 5.49 & 6.15 & 5.20 & 5.00\\
  2H-WSe$_{2}$ & 5.84 & 5.92 & 6.49 & 5.75 & 5.42\\
  2H-WTe$_{2}$ & 6.32 & 6.58 & 7.06 & 6.38 & 6.33\\
  \hline{}
\end{tabular}

\caption{Calculated $\delta_{\mathrm{2D}}$ from
  $\varepsilon_{\mathrm{SL}}^{\parallel}$ and
  $\varepsilon_{\mathrm{SL}}^{\perp}$, compared with the interlayer
  distance of corresponding bulk material $L_{\mathrm{SL}}$, the
  covalent thickness $\delta_{\mathrm{2D}}^{\mathrm{cov}}$, and
  $\alpha_{\mathrm{2D}}^{\perp}/\varepsilon_{0}$ for 2H TMDC materials.}
\label{tab:delta-L-DFt}
\end{table}

Another drawback of the 2D dielectric constant approach is the
overestimation of the out-of-plane dielectric response. As can be seen
in Figure \ref{fig:rescale-prb}, the extracted
$\varepsilon_{\mathrm{2D}}^{\perp}$ values for the TMDCs studied
are comparable or even larger than
$\varepsilon_{\mathrm{2D}}^{\parallel}$, which does not agree with the
physical picture that electrostatic screening of 2D materials are much
smaller perpendicular to the 2D plane. In fact, combining
Eq. \ref{eq:MG-effect-1} and the definition of $\alpha_{\mathrm{2D}}^{\perp}$, we
have:
\begin{equation}
  \label{eq:eps-alpha-perp}
  \frac{\alpha_{\mathrm{2D}}^{\perp}}{\varepsilon_{0}} = \delta_{\mathrm{2D}}(1 - (\varepsilon_{\mathrm{2D}}^{\perp})^{-1})
\end{equation}

\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.6\linewidth]{img/SI-eps-alpha-error.pdf}
  \caption{Calculated $\varepsilon_{\mathrm{2D}}^{\perp}$ value as a
    function of the difference between $\delta_{\mathrm{2D}}$ and
    $\alpha_{\mathrm{2D}}^{\perp}/\varepsilon_{0}$. A small change of
    $\alpha_{\mathrm{2D}}^{\perp}/\varepsilon_{0}$ chosen may lead to divergence of
    the $\varepsilon_{\mathrm{2D}}^{\perp}$ or even negative values,
    which is apparently unphysical}
  \label{fig:eps-alpha-error}
\end{figure}

which indicate that the characteristic length
$\alpha_{\mathrm{2D}}^{\perp}/\varepsilon_{0}$, is very close but slightly smaller
than $\delta_{\mathrm{2D}}$ estimated by the effective medium theory,
if $\varepsilon^{\perp}_{\mathrm{2D}} \gg 1$. Moreover, from
Eq. \ref{eq:eps-alpha-perp}, when $\delta_{\mathrm{2D}}$ and
$\alpha_{\mathrm{2D}}^{\perp}/\varepsilon_{0}$ are close, slight change of the
$\delta_{\mathrm{2D}}$ chosen may lead to divergence of
$\varepsilon_{\mathrm{2D}}^{\perp}$, as shown in Figure
\ref{fig:eps-alpha-error}. Therefore cautions must to taken when
treating the dielectric response of the 2D material using effective
medium theory. In comparison, the 2D polarizability does not require
the guess of the thickness, and therefore is the true descriptor of
the 2D dielectric nature.

To conclude, based on theoretical and technical considerations, there are several
advantages of using the polarizability $\alpha$ for describing the dielectric
nature of 2D materials, including
\begin{enumerate}
\item $\alpha_{\mathrm{2D}}$ can be used to describe both the local and macroscopic dielectric properties, while $\epsilon_{\mathrm{2D}}$ can't.
\item Calculating $\alpha_{\mathrm{2D}}$ only requires to calculate the dielectric response at single superlattice length, while $\epsilon_{\mathrm{2D}}$ requires calculation with varied superlattice length.
\item $\alpha_{\mathrm{2D}}$ correctly respresents the screening length of 2D material, while $\epsilon_{\mathrm{2D}}$ does not.
\item $\alpha_{\mathrm{2D}}$ correctly represents the different degree of screening in/out-of-plane, while $\epsilon_{\mathrm{2D}}$ does not.

\item The value of $\epsilon_{\mathrm{2D}}$ hugely depends on the
  choice of the thickness of 2D material, while such information is
  intrinsically embedded in $\alpha_{\mathrm{2D}}$.
\end{enumerate}

\subsection{Dependence of $\alpha_{\mathrm{2D}}$ on bandgap}
\label{sec:pol-2D-Eg}

In this section we further look into the bandgap dependency of the 2D
polarizability. Figure \ref{fig:SI-raw-HSE} shows the raw data of
$\alpha_{\mathrm{2D}}^{\parallel}$ and $\alpha_{\mathrm{2D}}^{\perp}$
as functions of $E_{\mathrm{g}}$ of the 2D materials investigated. We
observe that $\alpha_{\mathrm{2D}}^{\parallel}$ can be approximated by
a reciprocal function of $E_{\mathrm{g}}$, that
$\alpha_{\mathrm{2D}}^{\parallel}\sim{}
7.295(E_{\mathrm{g}})^{-1}$. On the other hand, the plot of
$\alpha_{\mathrm{2D}}^{\perp}$ against $E_{\mathrm{g}}$ shows no
apparent correlation.
\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.8\linewidth]{img/SI-alpha_EG_raw_HSE.pdf}
  \caption{$E_{\mathrm{g}}$-dependence of \textbf{a} $\alpha_{\mathrm{2D}}^{\parallel}$ and
    \textbf{b} $\alpha_{\mathrm{2D}}^{\perp}$ for the 2D materials investigated here.}
  \label{fig:SI-raw-HSE}
\end{figure}

\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.5\linewidth]{img/SI-compare_alpha_Eg.pdf}
  \caption{Relation between $1/\alpha_{\mathrm{2D}}^{\parallel}$ and various choices
    of $E_{\mathrm{g}}$: minimal gap from HSE06 (blue), minimal gap
    from PBE (orange) and direct gap from PBE (green). The linear
    regression results are shown as broken lines.}
  \label{fig:alpha-Eg-diff}
\end{figure}

We also investigate the relation of 2D polarizabilities with
difference choices of \textit{ab initio} bandgaps. It is widely
accepted that the PBE exchange correlation, tends to underestimate the
bangap \cite{Heyd_2005,Kumar_2016_PRB,Kumar_2016_jpcc}.  Indeed,
changing the choice of $E_{\mathrm{g}}$ yields different regression
relation with $1/\alpha_{\mathrm{2D}}^{\parallel}$, as shown in Figure
\ref{fig:alpha-Eg-diff}. We see that due to the underestimation of PBE
bandgap, the slope of linear regression is larger than that from
HSE-bandgap. We also observe that the $1/\alpha-E_{\mathrm{g}}$
relation is better presented by using the minimal HSE bandga than the
minimal PBE bandgap, due to higher regression $R^{2}$ coefficient of
the former. We note that the higher $R^{2}$ coefficient observed using
the direct PBE bandgap than the minimal PBE bandgap may be solely
caused by the fact that the direct bandgap of 2D materials on the PBE
level is closer to the HSE bandgap. From the random phase
approximation theory of dielectric response, the polarizability is
contributed by all possible transition between valence and conduction
bands, with the minimal bandgap as the least possible transition. In
this sense, $\alpha_{\mathrm{2D}}^{\parallel}$ is mostly like to be associated with
the minimal, not direct bandgap, as also observed in the original Moss
relation. We also examine the validity of such statement based on the
analysis of the Computational 2D Materials Database (C2DB)
\cite{Haastrup_2018}, as will be discussed in the following sections.

\section{Validation on the C2DB 2D materials database}
\subsection{Validation of the universal description of 2D polarizabilities}
\label{sec:gpaw-1}

\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.8\linewidth]{img/SI-gpaw-data.pdf}
  \caption{Validation the linear relation between \textbf{a}
    $1/\alpha_{\mathrm{2D}}^{\parallel}-E_{\mathrm{g}}(\mathrm{HSE})$ and \textbf{b}
    $\alpha_{\mathrm{2D}}^{\perp}-\delta_{\mathrm{cov}}$ on the C2DB 2D material
    database, corresponding to Figure 3b and 3c in main text.}
  \label{fig:gpaw-alpha-relation}
\end{figure}

Due to the high computation complexity of dielectric response
calculations on the HSE level, our 2D material database is limited to
about 50 types of materials. It is desirable to validate our proposed
relations on a even larger scale database. We select over 230
semiconducting 2D materials from the C2DB database with a GW bandgap
larger than 0.05 eV and extracted the 2D polarizabilities calculated
on the PBE level. The propsed linear relations between
$1/\alpha_{\mathrm{2D}}^{\parallel}-E_{\mathrm{g}}(\mathrm{HSE})$ and
$\alpha_{\mathrm{2D}}^{\perp}-\delta_{\mathrm{cov}}$ are also valid,
as shown in Figure \ref{fig:gpaw-alpha-relation}. Excellent linear
correlation is observed in both cases, with the $R^{2}$ coefficient
larger than 0.9, indicating the existence of the universal description
of 2D dielectric nature through the proposed relations with the 2D
polarizabilities. We note that the slope of linear regression is
slightly different from the our proposed relation from the dielectric
response on HSE06 level, due to the fact that the macroscopic
dielectric constant $\varepsilon_{\mathrm{SL}}$ calculated on the PBE
level is about slightly difference. Despite the minor deviation of the
slope of linear regression, the analysis on the C2DB database supports
our understanding of the universal dielectric nature of 2D materials.

@@

Next we investigate the influence of choice of $E_{\mathrm{g}}$ on the
regression of $\alpha_{\mathrm{2D}}^{\parallel}-E_{\mathrm{g}}$ relation. Figure
\ref{fig:SI-gpaw-alpha-Eg-all} shows $1/\alpha_{\mathrm{2D}}^{\parallel}$ from the
C2DB database as a function of minimal and direct bandgap calculated
on PBE, HSE06 and GW levels. We observe,
although the regression $R^{2}$ coefficient in all cases are around
0.9, the $\alpha_{\mathrm{2D}}^{\parallel}-E_{\mathrm{g}}$ is better described using
the HSE and GW bandgaps than the PBE bandgaps. On the other hand,
using indirect or minimal bandgaps on the same level gives almost
identical regression slope. The observations are in good agreement
with our calculations on the HSE level discussed in Section
\ref{sec:pol-2D-Eg}. In combination with the physical contribution of
$E_{\mathrm{g}}$ to the dielectric screening, we conclude that the
minimal bandgap should be used for quantitative prediction of the
in-plane 2D polarizability. The prediction is greatly improved when
more accurate theory level for bandgap is used (for instance, HSE and GW).

\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.95\linewidth]{img/SI-gpaw-alpha_Eg_all.pdf}
  \caption{$\alpha_{\mathrm{2D}}^{\parallel}$ as funtion of minimal and direct
    $E_{\mathrm{g}}$ calculated on different theoretical levels:
    \textbf{a} PBE, \textbf{b} HSE and \textbf{c} GW of the C2DB
    database.}
  \label{fig:SI-gpaw-alpha-Eg-all}
\end{figure}
